
```{r include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```
# External usage {-}

## Statement of need {-}
x
## How to adapt this course {-}

## License {-}

If you use this material for teaching, research or anything else please let me (Andy) know via [Twitter](https://twitter.com/andymaclachlan) or email --- a [dot] maclachlan [at] ucl [dot] ac [dot] uk).

This practical book is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International (CC BY-SA 4.0) License](https://creativecommons.org/licenses/by-sa/4.0/).
<center>
<i class="fab fa-creative-commons fa-2x"></i><i class="fab fa-creative-commons-by fa-2x"></i><i class="fab fa-creative-commons-sa fa-2x"></i>
</center>

You are free to: 

* **Share** — copy and redistribute the material in any medium or format

* **Adapt** — remix, transform, and build upon the material
for any purpose, even commercially.

However, you  give appropriate credit, provide a link to the license, and indicate if changes were made. If you remix, transform, or build upon the material, you must distribute your contributions under the same license as the original.

But, you do not have to comply with the license for elements of the material in the public domain or where your use is permitted by an applicable exception or limitation.

The code within this pracical book is available under the [MIT license](https://opensource.org/licenses/MIT); so it is free to use (for any purpose) as long as you cite the source.

## Version {-}

This is version 2.0 of the practical book


## Packages {-}

This bookdown document was built with:

```{r message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(devtools)
library(DT)

# needed because new_session is set to true in _bookdown.yml
all_pkgs <- renv::dependencies(path = "DESCRIPTION") %>% 
  pull(Package) 

session <- devtools::session_info(pkgs = all_pkgs)

session$platform
```

And makes use of the following packacges throughout. Thanks to [STAT 545](https://stat545.com/index.html#other-contributors) for this code.

```{r message = FALSE, warning = FALSE, echo = FALSE}
session$packages %>% 
  select(package, loadedversion, date, source) %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                filter = list(position = 'top'),
                options = list(pageLength = nrow(session$packages), 
                           autoWidth = TRUE,
                           bInfo = FALSE,
                           paging = FALSE))
```
