---
output:
  word_document: default
  pdf_document: default
  html_document: default
---
# External usage {-}

## Statement of need {-}

## How to adapt this course {-}

## License {-}

If you use this material for teaching, research or anything else please let me (Andy) know via [Twitter](https://twitter.com/andymaclachlan) or email --- a [dot] maclachlan [at] ucl [dot] ac [dot] uk).

This practical book is licensed under a [Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-nc-sa/4.0/).

The code within this pracical book is available under the [MIT license](https://opensource.org/licenses/MIT); so it is free to use (for any purpose) as long as you cite the source.

## Version {-}

This is version 2.0 of the practical book


## Packages {-}

This bookdown document was built with:

```{r message = FALSE, warning = FALSE, echo = FALSE}
library(tidyverse)
library(devtools)
library(DT)

# needed because new_session is set to true in _bookdown.yml
all_pkgs <- renv::dependencies(path = "DESCRIPTION") %>% 
  pull(Package) 

session <- devtools::session_info(pkgs = all_pkgs)

session$platform
```

And makes use of the following packacges throughout. Thanks to [STAT 545](https://stat545.com/index.html#other-contributors) for this code.

```{r message = FALSE, warning = FALSE, echo = FALSE}
session$packages %>% 
  select(package, loadedversion, date, source) %>% 
  DT::datatable(rownames = FALSE,
                class = 'cell-border stripe',
                filter = list(position = 'top'),
                options = list(pageLength = nrow(session$packages), 
                           autoWidth = TRUE,
                           bInfo = FALSE,
                           paging = FALSE))
```
